Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-15 edubots_surveys.Rnw
extends introduction with research questions refs #10

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.}\fnm{Francisco} \snm{Barranco}}<

@@

@@

>>>>

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.}\fnm{Francisco} \snm{Barranco}}

@@

% Maybe move it to a different place later
As a starting point, we have analyzed the responses to a survey from XXX teachers asking about their attitudes towards the use of chatbots in their classes. We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers willing to use chatbots in their classes? }
\item{ RQ2 - Which kind of chatbots are they interested in? }
\item{ RQ3 - Regarding technology acceptance, are there any differences regarding age, gender,  or years of experience in Education? }
\item{ RQ4 - } 
\end{itemize}

@@

Regarding the factors for the adoption of chatbots in Education, many studies have focused on the evaluation of technology acceptance or usability. However, Higher Education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
